---
title: "R Notebook"
output: html_notebook
---

# Final project

**Team**: Oleksii Mytnyk, Yaroslav Klym, Shevchenko Ivan

```{r message=FALSE}
require(BSDA)
library(BSDA)
require(EnvStats)
library(EnvStats)
library(dplyr)
library(tidyr)
```

## Sample data description

We decided to choose to analyze Steam PC game dataset.

```{r}
data = read.csv("games_data.csv")
data
```

## Distribution of price

We will test dependency between price and another parameters of the game.

Here we analyze the distribution of the price of the games and testing whether it have normal distribution. We used Kolmogorov test to check it and we see that this distribution is not normal as p-value is small.

```{r warning=FALSE}
data["price"][data["price"] == "Free to play"] <- 0
sample_data <- data
sample_data_with_price <- data %>% transform(price = as.numeric(gsub(",", "", price))) %>% filter(!is.na(price))
sigma2 <- 2 * sd(sample_data_with_price$price)
price_mean <- mean(sample_data_with_price$price)

price_data <- sample_data_with_price %>% filter(price <= price_mean + sigma2)
price_data <- price_data$price
plot(density(price_data))
print(paste("Mean:", mean(price_data)))
print(paste("Median:", median(price_data)))
print(paste("Variance:", var(price_data)))
print(paste("Skewness:", skewness(price_data)))
print(paste("Kurtosis:", kurtosis(price_data)))
ks.test(price_data, "pnorm", mean(price_data), sd(price_data))
```

## Hypothesis testing

### Testing price for different genres

Here we will search a dependency between genre of the game and it's price. In order to that we take average price of all games that are from searched genre.

```{r}
sample_data_by_genre <- sample_data_with_price %>% separate_rows(genres, sep = ";") %>% filter(gsub(" ", "", genres) != "")
grouped_data <- sample_data_by_genre %>% group_by(genres) %>% filter(10 < n()) %>% summarise_at(vars(price), list(average_price = mean))

grouped_data[order(grouped_data$average_price), ]
```

#### 1. Racing costs more than Adventure

Here we test whether racing games costs more than adventure. We use t-test, as we want to compare two means and we don't have population variance.

```{r}
sample_racing <- (sample_data_by_genre %>% filter(genres == "Racing"))$price
sample_adventure <- (sample_data_by_genre %>% filter(genres == "Adventure"))$price
t.test(x = sample_racing, y = sample_adventure, alternative = "l")
```

Since the p-value is large, **racing games are more expensive than adventure games**.

#### 2. Indie games are cheaper in general

Here we test whether indie games costs less than average game. We use t-test, as we want to compare two means and we don't have population variance.

```{r}
sample_indie <- (sample_data_by_genre %>% filter(genres == "Indie"))$price
sample_all <- (sample_data_by_genre)$price
t.test(x = sample_indie, y = sample_all, alternative = "g")
```

Since the p-value is large, **indie games are cheaper than average**.

#### 3. Racing games are expensive

Here we test whether racing games costs more than average game. We use t-test, as we want to compare two means and we don't have population variance.

```{r}
sample_racing <- (sample_data_by_genre %>% filter(genres == "Racing"))$price
sample_all <- (sample_data_by_genre)$price
t.test(x = sample_racing, y = sample_all, alternative = "l")
```

Since the p-value is large, **racing games are more expensive than average**.

### Testing positive reviews percentage for different developers

```{r}
sample_data_with_reviews <- sample_data %>% transform(percent_positive = as.numeric(gsub("%", "", percent_positive))) %>% filter(!is.na(percent_positive)) %>% filter(reviews > 1000)
sample_data_by_developer <- sample_data_with_reviews %>% filter(gsub(" ", "", developer) != "")

grouped_data <- sample_data_by_developer %>% group_by(developer) %>% filter(3 < n()) %>% summarise_at(vars(percent_positive), list(average_percent_positive = mean))

grouped_data[order(grouped_data$average_percent_positive, decreasing = T), ]
```

#### 4. CD PROJEKT RED has more positive reviews than Ubisoft

Here we test whether CD PROJEKT RED has more positive reviews than Ubisoft. We use t-test, as we want to compare two means and we don't have population variance.

```{r}
sample_red <- (sample_data_by_developer %>% filter(developer == "CD PROJEKT RED"))$percent_positive
sample_ubisoft <- (sample_data_by_developer %>% filter(developer == "Ubisoft Montreal"))$percent_positive
t.test(x = sample_red, y = sample_ubisoft, alternative = "l")
```

Since the p-value is large, **CD PROJEKT RED has more positive reviews than Ubisoft**.

### Testing price for different game modes

#### 5. Testing price for single-player, multi-player

Here we will search a dependency between whether game is single-player or multi-player and it's price. In order to that we take average price of all games that are from searched type.

```{r}
sample_data_by_ms <- sample_data_with_price %>% separate_rows(multiplayer_or_singleplayer, sep = ";") %>% filter(gsub(" ", "",multiplayer_or_singleplayer) != "")
grouped_data <- sample_data_by_ms %>% group_by(multiplayer_or_singleplayer) %>% filter(10 < n())  %>% summarise_at(vars(price), list(average_price = mean))

player <- c('Single-player', 'Multi-player')

grouped_data[grouped_data$multiplayer_or_singleplayer %in% player, ]
```

#### 6. Multi-player games are more expensive then Single-player

Here we test whether multiplayer games costs more than single-player game. We use t-test, as we want to compare two means and we don't have population variance.

```{r}
multi.player <- (sample_data_by_ms %>% filter(multiplayer_or_singleplayer == 'Multi-player'))$price
single.player <- (sample_data_by_ms %>% filter(multiplayer_or_singleplayer == 'Single-player'))$price
t.test(x = multi.player, y = single.player, alternative = 'g')
```
